Assessment and Optimization of Nowcast Measures for Trend Detection

### 2023-12-05 paper.tex
Update draft, correct prob. measures

\begin{itemize}
	\item Trending is an important feature of nowcasts to be identify changes in the situation before the actual quantity can be measured
	\item Examples: Covid, BIP, Medicine, ... 
\end{itemize}

@@

\begin{itemize}
  \item Translate into mathematical notation
  \item Illustrative Example: Two nowcasts of quantity of interest, where one jumps up and down and one points in right direction with the same rmse
\end{itemize}

@@

\begin{itemize}
  \item Quadratic/Brier Score for $k$ possible outcomes: \begin{equation}
  S((p_1, \dots, p_k), i) = 2 p_i - \sum_{l=1}^k p_i^2 - 1;
\end{equation}
for dichotomous outcomes ($p_1 = \hat{P}(\ydiff_t > 0)$: probability for $\ydiff_t > 0$):
\begin{equation}
  S(p_1, \ydiff_t) = p_1 \ind{\ydiff_t > 0} + (1 - p_1) (1 - \ind{\ydiff_t > 0}) + p_1^2 + (1-p_1)^2 - 1
\end{equation}
\end{itemize}
\item Probabilistic versions of non-probabilistic measures:
\begin{itemize}
  \item Assume an additive error decomposition for both observation and nowcast to account for non-systematic and short-term (i.e., intra-day) effects:
  	\begin{align}
  		\ydiff_t &= \ydifft + \varepsilon_t^y \\
  		\xdiff_t &= \xdifft + \varepsilon_t^x
	\end{align}
\item  Replace indicators in the above formulations by the corresponding probabilities:
\begin{align}
		\mprob_{\text{acc}} &= \frac{\sum_{t=2}^T \Prob{ \ydifft_t > 0, \xdifft_t > 0} + \sum_{t=2}^T \Prob{\ydifft_t < 0, \xdifft_t < 0}}{T-1}  \\
   \mprob_{\text{py}} &= \frac{\sum_{t=2}^T \Prob{\ydifft_t > 0, \xdifft_t > 0}}{\sum_{t=2}^T \Prob{\ydifft_t > 0}} = \sum_{t=2}^T \frac{\Prob{\ydifft_t > 0, \xdifft_t > 0}}{\Prob{\ydifft_t > 0}} = \sum_{t=2}^T \Prob{\xdifft_t > 0 | \ydifft_t > 0} \\
    \mprob_{\text{px}} &= \frac{\sum_{t=2}^T \Prob{\ydifft_t > 0, \xdifft_t > 0}}{\sum_{t=2}^T \Prob{\xdifft_t > 0}} = \sum_{t=2}^T \Prob{\ydifft_t > 0 | \xdifft_t > 0} \\
    \mprob_{\text{ny}} &= \frac{\sum_{t=2}^T \Prob{\ydifft_t < 0, \xdifft_t < 0}}{\sum_{t=2}^T \Prob{\ydifft_t < 0}} = \sum_{t=2}^T \Prob{\xdifft_t < 0 | \ydifft_t < 0} \\
    \mprob_{\text{px}} &= \frac{\sum_{t=2}^T \Prob{\ydifft_t < 0, \xdifft_t < 0}}{\sum_{t=2}^T \Prob{\xdifft_t < 0}} = \sum_{t=2}^T \Prob{\ydifft_t < 0 | \xdifft_t < 0}
\end{align}
\item Simple error model:
  \begin{align}
	  \varepsilon_Y \sim N(0, \sigma_Y) \\
	  \varepsilon_X \sim N(0, \sigma_X)
  \end{align}
  yields, e.g.,
  	\begin{equation}
  		\mprob_{\text{acc}} = \frac{\sum_{t=2}^T  \big( 1 - \Phi_{\ydiff_t, \sigma_y}(0) - \Phi_{\xdiff_t, \sigma_x} (0) + 2 \Phi_{(\ydiff_t, \xdiff_t); (\sigma_y, \sigma_x)}( 0, 0) \big) }{T-1}, 
	\end{equation}
	where $\Phi$ denotes a (possibly multivariate) normal distribution
\end{itemize}
\end{itemize}

\subsection{Confidence intervals for the measures}

@@

@@

>>>>

\begin{itemize}
	\item Trending is an important feature of nowcasts to be identify changes in the situation before the actual quantity can be measured
	\item What scores are currently used?
	\item Examples: Covid, BIP, Medicine, ... 
\end{itemize}

@@

\begin{itemize}
  \item Translate into mathematical notation
  \item Illustrative Example: Two nowcasts of quantity of interest, where one jumps up and down and one points in right direction with the same rmse; small subset of Simulation~\ref{sec:simulation_rmse_mae}; Plot time series \& time series of differences
\end{itemize}

\subsection{Graphical methods}

\begin{itemize}
  \item 4Q-Plot
  \item Andere Medizin-Plots mit Verweis auf Grothe-Paper
\end{itemize}

@@

\begin{itemize}
  \item Quadratic/Brier Score for $k$ possible outcomes: \begin{equation}
  S((p_1, \dots, p_k), i) = 2 p_i - \sum_{l=1}^k p_i^2 - 1;
\end{equation}
for dichotomous outcomes ($p_1 = \hat{P}(\ydiff_t > 0)$: probability for $\ydiff_t > 0$):
\begin{equation}
  S(p_1, \ydiff_t) = p_1 \ind{\ydiff_t > 0} + (1 - p_1) (1 - \ind{\ydiff_t > 0}) + p_1^2 + (1-p_1)^2 - 1
\end{equation}
\end{itemize}
\item Probabilistic versions of non-probabilistic measures:
\begin{itemize}
  \item Assume an additive error decomposition for both observation and nowcast to account for non-systematic and short-term (i.e., intra-day) effects:
  	\begin{align}
  		\ydiff_t &= \ydifft + \varepsilon_t^y \\
  		\xdiff_t &= \xdifft + \varepsilon_t^x
	\end{align}
\item  Replace indicators in the above formulations by the corresponding probabilities:
\begin{align}
		\mprob_{\text{acc}} &= \frac{\sum_{t=2}^T \Prob{ \ydifft_t > 0, \xdifft_t > 0} + \sum_{t=2}^T \Prob{\ydifft_t < 0, \xdifft_t < 0}}{T-1}  \\
   \mprob_{\text{py}} &= \frac{\sum_{t=2}^T \Prob{\ydifft_t > 0, \xdifft_t > 0}}{\sum_{t=2}^T \Prob{\ydifft_t > 0}} \\
    \mprob_{\text{px}} &= \frac{\sum_{t=2}^T \Prob{\ydifft_t > 0, \xdifft_t > 0}}{\sum_{t=2}^T \Prob{\xdifft_t > 0}} \\
    \mprob_{\text{ny}} &= \frac{\sum_{t=2}^T \Prob{\ydifft_t < 0, \xdifft_t < 0}}{\sum_{t=2}^T \Prob{\ydifft_t < 0}} \\
    \mprob_{\text{px}} &= \frac{\sum_{t=2}^T \Prob{\ydifft_t < 0, \xdifft_t < 0}}{\sum_{t=2}^T \Prob{\xdifft_t < 0}} 
\end{align}
\item Simple error model:
  \begin{align}
	  \varepsilon_Y \sim N(0, \sigma_Y) \\
	  \varepsilon_X \sim N(0, \sigma_X)
  \end{align}
  yields, e.g.,
  	\begin{equation}
  		\mprob_{\text{acc}} = \frac{\sum_{t=2}^T  \big( 1 - \Phi_{\ydiff_t, \sigma_y}(0) - \Phi_{\xdiff_t, \sigma_x} (0) + 2 \Phi_{(\ydiff_t, \xdiff_t); (\sigma_y, \sigma_x)}( 0, 0) \big) }{T-1}, 
	\end{equation}
	where $\Phi$ denotes a (possibly multivariate) normal distribution
\end{itemize}
\end{itemize}

\subsection{Confidence intervals and missing data}

\begin{itemize}
  \item Bootstrapping: Describe approach (Simple bootstrap or multiplier?)
  \item Missing data
\end{itemize}

@@

\subsection{Effect of increasing sample size?}

\subsection{Simulation: Bootstrap}

Question: How well does bootstrap approach perform?

\begin{itemize}
  \item 
\end{itemize}

@@

\subsection{Nowcasts for the COVID infections in Germany}

\begin{itemize}
  \item Describe QoI and Nowcasts; which nowcasts do we consider? Which data is available when?
  \item Plot data
\end{itemize}

\subsection{Nowcasting of GDP}
